---
title: "Linear-Model-With-Prediction"
author: "Colton Beardsley"
date: "Fall 2023"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
---


```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
```

```{r, eval=TRUE,warning=FALSE}
url <- "https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt" 
data <- read.csv(file=url,sep="",header=TRUE) 
```

# Introduction

$H_0$ There is no meaningful difference in the data
$H_A$ There is a meaningful difference within the data


# Methods

We will be using the CandP helper file Num-NUm to help us run tests on the data we've imported from the textbook.


# Results



## Graphical

```{r}
ggplot(data,aes(y=ARM,x=SIMS))+
 geom_point()+
 geom_smooth(method=lm)
ggplot(data,aes(y=GRIP,x=SIMS))+
 geom_point()+
 geom_smooth(method=lm)
ggplot(data,aes(y=ARM+GRIP,x=SIMS))+
 geom_point()+
 geom_smooth(method=lm)
```




## Numerical

```{r}
cor(SIMS~ARM,data=data)
cor(SIMS~GRIP,data=data)
cor(SIMS~ARM+GRIP,data=data)

```



## Inferential

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```

Based on the data shown, model 3 is the best option. The residual standard error is the lowest. The adjusted R-squared is the closest to 1.

# Conclusion

We can confidently reject the null hypothesis suggesting no relationship between the data. Examination of the scatter plot's regression lines clearly illustrates an overall positive correlation in the data. Furthermore, the correlation coefficients, being closer to one than zero, affirm the presence of a significant relationship. To determine the best-fitting model, we conducted a thorough evaluation, comparing adjusted R-squared values, residual standard errors, and utilizing the predict function to assess the width of confidence intervals. Model three consistently outperformed the other models in all categories and was further corroborated by a one-way ANOVA, where it yielded the lowest P-value among the options.


Based on our findings, we can assert that physical strength serves as a robust indicator of job performance in this study, with the combination of arm and grip strength emerging as the most effective predictor from the provided data.

