---
title: "Linear-Model-With-Prediction"
author: "Colton Beardsley"
date: "Fall 2023"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
---


```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
```

```{r, eval=TRUE,warning=FALSE}
url <- "https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt" 
data <- read.csv(file=url,sep="",header=TRUE) 
```

# Introduction

$H_0$ There is no meaningful difference in the data
$H_A$ There is a meaningful difference within the data


# Methods

We will be using the CandP helper file Num-NUm to help us run tests on the data we've imported from the textbook.


# Results



## Graphical

```{r}
ggplot(data,aes(y=ARM,x=SIMS))+
 geom_point()+
 geom_smooth(method=lm)
ggplot(data,aes(y=GRIP,x=SIMS))+
 geom_point()+
 geom_smooth(method=lm)
ggplot(data,aes(y=ARM+GRIP,x=SIMS))+
 geom_point()+
 geom_smooth(method=lm)
```




## Numerical

```{r}
cor(SIMS~ARM,data=data)
cor(SIMS~GRIP,data=data)
cor(SIMS~ARM+GRIP,data=data)
```



## Inferential

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```

Based on the data shown, model 3 is the best option. The residual standard error is the lowest. The adjusted R-squared is the closest to 1.

# Conclusion



